---
title: "Log and Box-Cox Transforms"
output: html_notebook
---
[Scott Burk's Video](https://www.youtube.com/watch?v=HzjolWoxjPI&list=PLX-TyAzMwGs-I3i5uiCin37VFMSy4c50F&index=4)

**Box-Cox Transform**

$w_t = \begin{gather}\begin{cases}log(y_t) & \text{if  }\lambda = 0;\\(y_t^\lambda-1)/\lambda & \text{otherwise;}\end{cases}\end{gather}$

**Inverse or Back-Transform**

Used to re-scale back to original time series

$y_t = \begin{gather}\begin{cases}exp(w_t) & \text{if  }\lambda = 0;\\(\lambda w_t+1)^{1/\lambda} & \text{otherwise;}\end{cases}\end{gather}$

**Raw data**
```{r}
library(fpp)
plot(elec,
     ylab = "Raw electricity demand",
     xlab = "Year",
     main = "Raw monthly electricity demand")
title(main = "Raw", line = -1)
```
Notice the increase in variation over time. This is not desirable so we can use the log.

**Log of data**
```{r}
plot(log(elec),
     ylab = "Transformed electricity demand",
     xlab = "Year",
     main = "Transformed monthly electricity demand")
title(main = "Raw", line = -1)
```
This is better but towards the end of the series variability seems to change

**Box-Cox**

We need a lambda. We will let R provide one with `BoxCox.lambda`
```{r}
lambda <- BoxCox.lambda(elec) # 0.265
plot(BoxCox(elec, lambda))
```
**Calendar Adjustments**

Take into account eg. workdays, variability in days of the month.
```{r}
monthdays <- rep(c(31,28,31,30,31,30,31,31,30,31,30,31),14) # 14 years of data
monthdays[26 + (4*12)*(0:2)] <- 29
par(mfrow = c(2,1))
plot(milk,
     main = "Monthly milk production per cow",
     ylab = "Pounds",
     xlab = "Years")
plot(milk/monthdays,
     main = "Average milk production per cow per day",
     ylab = "Pounds",
     xlab = "Years")
```
This clearly gives a smoother time series

Other transformations should be used to take into account for example:

**Population Adjustments** to account for variation in population size

*Inflation Adjustments**


















