---
title: "X11 Decomposition"
output:
  html_document:
    df_print: paged
  github_document:
    toc: true
---

[Scott Burk's Video](https://www.youtube.com/watch?v=1zMvAKX2xeQ&list=PLX-TyAzMwGs-I3i5uiCin37VFMSy4c50F&index=10)

```{r}
library(fpp2)
```

# X11 Decomposition

* Based on classical decomposition
* Includes additional steps/features
* Trend-cycle estimates available for all observations including end points
* Seasonal component allowed to vary slowly over time
* Methods for handling trading day variation, holiday effects, other effects of known predictors
* Both additive and multiplicative
* Highly robust to outliers and level shifts in the time series

```{r}
# install.packages("seasonal")
library(seasonal)
```

```{r}
elecequip %>%
  seas(x11 = "") -> fit
autoplot(fit) +
  ggtitle("X11 Decomposition of Electrical Equipment Index")
```


```{r}
elecequip %>% 
  decompose(type = "multiplicative") %>%
    autoplot() +
    xlab("Year") +
    ggtitle("Multiplicative Decomposition of Electrical Equipment Index")
```

