---
title: "Seasonal and Trend Decomposition with Loess (STL)"
output:
  github_document:
    toc: true
  html_document:
    toc: true
    df_print: paged
---

[Scott Burk's Video](https://www.youtube.com/watch?v=DZ403FNW2YI&list=PLX-TyAzMwGs-I3i5uiCin37VFMSy4c50F&index=12)

* Handles any type of seasonality, not just monthly and quarterly
* The seasonal component can vary over time with a rate of change controlled by the user
* The smoothness of the trend cycle can be controlled by the user
* It can be robust to outliers
* Does not handle calendar variation automatically
* Only provides additive decompositions

```{r}
library(fpp2)
```
```{r}
elecequip %>%
  stl(t.window = 13,
      s.window = "periodic",
      robust = TRUE) %>%
  autoplot()
```

We still have a patch of remainders in 2009 that is unpleasant

```{r}
elecequip %>%
  stl(t.window = 17,
      s.window = "periodic",
      robust = TRUE) %>%
  autoplot()
```

Even worse.

```{r}
elecequip %>%
  stl(t.window = 7,
      s.window = "periodic",
      robust = TRUE) %>%
  autoplot()
```

Much better by adjusting the trend window.

```{r}
elecequip %>%
  stl(t.window = 7,
      s.window = 7,
      robust = TRUE) %>%
  autoplot()
```

Explicitly setting the seasonality window improved the remaineders even more although there are still sharp spikes.

```{r}
elecequip %>%
  stl(t.window = 7,
      s.window = 17,
      robust = TRUE) %>%
  autoplot()
```