---
title: "Forecasting with Exponential Smoothing"
output:
  github_document:
    toc: true
  html_document:
    toc: true
    df_print: paged
---

[Scott Burk's Video](https://www.youtube.com/watch?v=aquvCL3_6pI&list=PLX-TyAzMwGs-I3i5uiCin37VFMSy4c50F&index=14)



* $0 <= \alpha <=1$ is the smoothing parameter
  * Larger $\alpha$ gives more weight on $y_T$ and quicker dampening, smaller is closer to equal weight
* Weighted Averages of Past Observations
* Weights decay exponentially
* Simple Exponential Smoothing (SES)
  * Applicable when no clear trend or seasonal pattern exists
* Weighted Average method

$$
\begin{equation*}
\begin{aligned}
\hat{y}_{2/1} &= \alpha y_1+ (1- \alpha)l_0 \\
\hat{y}_{3/2} &= \alpha y_2+ (1- \alpha)\hat{y}_{2/1} \\
\hat{y}_{4/3} &= \alpha y_3+ (1- \alpha)\hat{y}_{3/2} \\
\vdots \\
\hat{y}_{T/T-1} &= \alpha y_{T-1}+ (1- \alpha)\hat{y}_{T-1/T-2} \\
\hat{y}_{T+1/T} &= \alpha y_T+ (1- \alpha)\hat{y}_{T/T-1} \\
\end{aligned}
\end{equation*}
\hat{y}_{T+1/T} = \sum_{j=0}^{T-1} \alpha (1-\alpha)^jy_{T-j} + (1-\alpha)^Tl_0 
$$

* Component Form

  * Forecast equation: $\hat{y}_{t-h/t}=L_t$
  
  * Smoothing equation: $L_t=\alpha y_t + (1-\alpha)L_{t-1}$

* Flat Forecasts

$$\hat{y}_{T+h/T}=\hat{y}_{T+1/T}=l_T, \quad  h = 2,3,\dots$$

* Other variations
  * Naive method
  * Average method

* Optimization to determine alpha and initial level

$$SSE = \sum_{t=1}^T(y_t-\hat{y}_{t/t-1})^2=\sum_{t=1}^Te_t^2$$

```{r}
library(fpp2)

oildata <- window(oil, start = 1996)
autoplot(oildata) +
  ylab("Oil (millions of tonnes)") +
  xlab("Year")
```

This data has no trend or seasonality so lends itself to exponential smoothing.

Estimate the parameters:

```{r}
fc <- ses(oildata, h=5)
round(accuracy(fc), 2)
```


```{r}
oilest <- ses(oildata, initial = "simple", h = 4)
oilest_alpha <- oilest$model$par["alpha"]
oilest_alpha
```

```{r}
forecast(fc)
```

```{r}
summary(fc)
```





