---
title: "Holt's Linear Trend"
output:
  github_document:
    toc: true
  html_document:
    toc: true
    df_print: paged
---

[Scott Burk's Video](https://www.youtube.com/watch?v=Nrt3kNEHb4I&list=PLX-TyAzMwGs-I3i5uiCin37VFMSy4c50F&index=15)

# The Method

Consists of a forecast equation and two smoothing equations

$$
\begin{align}
\text{Forecast equation} \quad & \hat{y}_{t+h/t} = l_t + hb_t \\
\text{Level equation} \quad & l_t = \alpha y_t+(1-\alpha)(l_{t-1} + b_{t-1}) \\
\text{Trend equation} \quad & b_t=\beta^*(l_1-l_{1-t})+(1-\beta^*)b_{t-1}
\end{align}
$$

$\alpha$ and $\beta^*$ are smoothing functions with domain $[0,1]$

```{r}
library(fpp2)
ausair
```

```{r}
air <- window(ausair, start = 1990)
fc <- holt(air, h=5)
summary(fc)
```

# Damped trend methods

Adds an additional time-dampening parameter $\phi$

$$
\begin{align}
\hat{y}_{t+h/t} &= l_t+(\phi+\phi^2+\dots+\phi^h)g_1 \\
l_t &= \alpha y_t + (1 - \alpha)(l_{t-1} + \phi b_{t-1}) \\
b_t &= \beta^*(l_1 - l_{t-1}) + (1 - \beta^*)\phi b_{t-1})
\end{align}
$$

```{r}
fc <- holt(air, h=5)
fc2 <- holt(air, damped = TRUE, phi =  0.9, h = 15)
autoplot(air) +
  autolayer(fc, series = "Holt's Method", PI = FALSE) +
  autolayer(fc2, series = "Damped Holt's Method", PI = FALSE) +
  ggtitle("Forecasts from Holt's Method") +
  ylab("Air passengers in Australia (millions)") +
  guides(colour = guide_legend(title = "Forecast"))
```

# Combine with smoothing

```{r}
autoplot(livestock) +
  xlab("Year") +
  ylab("Sheep in Asia (millions)")
```

## Cross Validation

```{r}
e_ses <- tsCV(livestock, ses, h=1)
e_holt <- tsCV(livestock, holt, h=1)
e_holtd <- tsCV(livestock, holt, damped=TRUE, h=1)
```

`tsCV()` does times series cross-validataion

## Mean squared error

```{r}
mean(e_ses^2, na.rm = TRUE)
```
```{r}
mean(e_holt^2, na.rm = TRUE)
```
```{r}
mean(e_holtd^2, na.rm = TRUE)
```

The dampened Holt method gave the least mean squared error

## Mean Absolute Error

```{r}
mean(abs(e_ses), na.rm = TRUE)
```

```{r}
mean(abs(e_holt), na.rm = TRUE)
```

```{r}
mean(abs(e_holtd), na.rm = TRUE)
```

```{r}
fc <- holt(livestock, damped=TRUE)
fc
```

```{r}
fc$model
```

$\alpha$ and $\phi$ are close to 1 and $\beta$ is close to 0

```{r}
autoplot(fc) +
  xlab("Year") +
  ylab("Sheep in Asia (millions)")
```


